%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
% !TeX spellcheck = en
\documentclass{resume} % Use the custom resume.cls style
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=cyan,      
    urlcolor=cyan,
}

\urlstyle{same}

\usepackage[left=0.75in,top=0.52in,right=0.75in,bottom=0.52in]{geometry} % Document margins
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref}
\usepackage{marvosym}
\usepackage{graphicx}

\name{Shivam Singhal}
\address{\href{https://championshuttler.com/}{championshuttler.com} \\
         \href{mailto:shivams2799@gmail.com}{shivams2799@gmail.com}\ \\
         \href{https://www.linkedin.com/in/championshuttler/}{in/championshuttler} \\
         \href{https://github.com/championshuttler/}{github.com/championshuttler} \\
         +91-8076797518}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
  \begin{rSummarySection}
  {
    \item Experience with frontend web development and open source development.
    \item JavaScript, Python, Docker, React, Git, Mercurial.
  }
  \end{rSummarySection}
\end{rSection}

%----------------------------------------------------------------------------------------
% WORK SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
    \begin{rWorkSection}{Hackerrank}
                           {Bangalore}
                           {SDE Intern}
                           {Jan '20 -- Present}
  {
    \item Implemented Employer Branding Settings in Hackerrank for Work platform to brand better.
    \item Implemented Interview Preparation Kit in Hackerrank for Community to prepare for Interviews.
.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{The Linux Foundation}
                           {Remote}
                           {Open Mainframe Intern}
                           {Sep '19 -- Dec 19}
  {
    \item Building frontend for Compliance engine is an analytical tool designed for an inspection and audit of data held on a Blockchain ledger. \href{https://github.com/openmainframeproject-internship/Compliance-Engine-2019/}{Project's Repository}.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{Mozilla}
                      {Remote}
                      {Google Summer of Code Student}
                      {May -- Sep '19}
  {
    \item Improved infrastructure underpinning Firefox's in-tree documentation via enabling linters, faster build times. \href{http://bit.ly/GSoC19FF}{GSoC Work Report}.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{Dadpreneur}
                     {New Delhi, IN}
                     {Software Development Intern}
                     {Jan -- March '19}
  {
    \item Rewrote referral invites system, with shareable url to expand reach of platform.
  }
  \end{rWorkSection}

  \begin{rWorkSection}{Eulercoder}
                     {Remote}
                     {Contract Developer}
                     {1 week '18}
  {
    \item Worked on frontend for admin in React.
  }
  \end{rWorkSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}
  \begin{rProjectSection}
    \item \textbf {create-web-ext} -- Scaffolding CLI tool for browser extensions. Written in \href{https://github.com/web-ext-labs/create-web-ext}{JavaScript}
    \item \textbf {Permission Inspector} --   Missing addon manager for firefox. Written in \href{https://github.com/tsl143/addonManager}{JavaScript}
    \item \textbf {webextensions.tech} -- UI for create-web-ext. Code can be \href{https://github.com/web-ext-labs/ui-tool}{found here}
    \item My other projects can be \href{hhttps://championshuttler.com/#projects/}{found here}
  \end{rProjectSection}

  \begin{rBlurbSection}
    \item {\em Open-source contributions:}
      I am an active OSS contributor, majorly in Mozilla. My \href{https://github.com/issues?q=is%3Apr+author%3Achampionshuttler}{\textbf{Merged PR's}}.
  \end{rBlurbSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	Talks Section
%----------------------------------------------------------------------------------------

\begin{rSection}{Talks}
  \begin{rProjectSection}
    \item \textbf {The Linux Foundation, Open Source Summit, France} -- Gave a talk on my Open Mainframe project.
  \end{rProjectSection}
  \begin{rProjectSection}
    \item \textbf {RedHat, DevConf, Bangalore} -- Gave a talk on Cross Browser Development.
  \end{rProjectSection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	VOLUNTEER EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Volunteer Experience}
  \begin{tabular}{rll}
2016	     & {\href{https://github.com/moz-niec/}{Mozilla Campus Club}}  & Lead the Mozilla Campus Club.\\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
  \begin{rEducationSection}{Guru Gobind Singh Indraprastha University, Delhi}
                           {Aug '16 -- Present}
                           {Bachelor of Technology in Computer Science and Engineering}
  \end{rEducationSection}
\end{rSection}

\end{document}
